---
title: "Craft Beer"
author: "Santiago Tellez"
date: "1/25/2019"
output: pdf_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Loading Packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load('stringr',
               'knitr',
               'ggplot2',
               'astsa',
               'lubridate',
               'ggmap',
               'maps',
               'mapdata',
               'dplyr',
               'gridExtra',
               'caret')
tfecho <- FALSE
```

#Loading Data
```{r, echo=tfecho}
opts_knit$set(root.dir = normalizePath("../"))

beers <- read.csv("craft-cans/beers.csv", stringsAsFactors = FALSE)
breweries <- read.csv("craft-cans/breweries.csv", stringsAsFactors = FALSE)

beers_and_brewery <- merge(beers, breweries, by.x = "brewery_id", by.y = "X")
colnames(beers_and_brewery)[c(6, 9)] <- c("name_beer", "name_brewery")
beers_and_brewery$state <- gsub(" ", "", beers_and_brewery$state)
```

#EDA
```{r, echo=tfecho}
abv_hist <- ggplot(data = beers_and_brewery[which(!is.na(beers_and_brewery$abv)), ]) +
  geom_histogram(aes(abv), fill = "dark green", binwidth = .003) + 
  ggtitle("ABV Histogram") +
  guides(fill = FALSE) +
  xlab("ABV") +
  ylab("Frequency") +
  theme(plot.title = element_text(hjust = 0.5))

ibu_hist <- ggplot(data = beers_and_brewery[which(!is.na(beers_and_brewery$ibu)), ]) +
  geom_histogram(aes(ibu), fill = "navy", binwidth = 5) + 
  ggtitle("IBU Histogram") +
  guides(fill = FALSE) +
  xlab("IBU") +
  ylab("Frequency") +
  theme(plot.title = element_text(hjust = 0.5))

oz_hist <- ggplot(data = beers_and_brewery[which(!is.na(beers_and_brewery$ounces)), ]) +
  geom_histogram(aes(ounces), fill = "red", binwidth = 2) + 
  ggtitle("Ounces Histogram") +
  guides(fill = FALSE) +
  xlab("Ounces") +
  ylab("Frequency") +
  theme(plot.title = element_text(hjust = 0.5))

state_chart <- ggplot(data = beers_and_brewery) +
  geom_bar(aes(state), stat = "count") + 
  ggtitle("State Count") +
  guides(fill = FALSE) +
  xlab("State") +
  ylab("Frequency") +
  theme(plot.title = element_text(hjust = 0.5))

grid.arrange(abv_hist, ibu_hist, oz_hist, nrow = 1)
state_chart
```

```{r, echo=FALSE}
abv_ibu <- ggplot(data = beers_and_brewery) +
  geom_point(aes(abv, ibu), na.rm = TRUE) +
  ggtitle("ABV vs. IBU") +
  xlab("ABV") +
  ylab("IBU") +
  theme(plot.title = element_text(hjust = 0.5))

abv_oz <- ggplot(data = beers_and_brewery) +
  geom_boxplot(aes(as.factor(ounces), abv), na.rm = TRUE) +
  ggtitle("ABV vs. Ounces") +
  xlab("Ounces") +
  ylab("ABV") +
  theme(plot.title = element_text(hjust = 0.5))

ibu_oz <- ggplot(data = beers_and_brewery) +
  geom_boxplot(aes(as.factor(ounces), ibu), na.rm = TRUE) +
  ggtitle("IBU vs. Ounces") +
  xlab("Ounces") +
  ylab("IBU") +
  theme(plot.title = element_text(hjust = 0.5))
```

#Label Creation - Reducing Factor Levels in Style

We created 8 main categories for beer type:

* Ale
* India Pale Ale
* Lager
* Kölsch
* Stout
* Wheat
* Fruit
* Other

```{r, echo=tfecho, message=FALSE}
beers_and_brewery$type <- NA
beers_and_brewery$type[which(grepl("Ale", beers_and_brewery$style))] <- "ale"
beers_and_brewery$type[which(grepl("IPA", beers_and_brewery$style))] <- "ipa"
beers_and_brewery$type[which(grepl("India", beers_and_brewery$style))] <- "ipa"
beers_and_brewery$type[which(grepl("Lager", beers_and_brewery$style))] <- "lager"
beers_and_brewery$type[which(grepl("Stout", beers_and_brewery$style))] <- "stout"
beers_and_brewery$type[which(grepl("Porter", beers_and_brewery$style))] <- "stout"
beers_and_brewery$type[which(grepl("Malt", beers_and_brewery$style))] <- "other"
beers_and_brewery$type[which(grepl("Kölsch", beers_and_brewery$style))] <- "kolsch"
beers_and_brewery$type[which(grepl("Pilsner", beers_and_brewery$style))] <- "lager"
beers_and_brewery$type[which(grepl("Pilsener", beers_and_brewery$style))] <- "lager"
beers_and_brewery$type[which(grepl("Fruit", beers_and_brewery$style))] <- "fruit"
beers_and_brewery$type[which(grepl("Cider", beers_and_brewery$style))] <- "other"
beers_and_brewery$type[which(grepl("Witbier", beers_and_brewery$style))] <- "wheat"
beers_and_brewery$type[which(grepl("Rye", beers_and_brewery$style))] <- "other"
beers_and_brewery$type[which(grepl("Hefeweizen", beers_and_brewery$style))] <- "wheat"
beers_and_brewery$type[which(is.na(beers_and_brewery$type))] <- "other"

table(beers_and_brewery$type)
```

We also grouped the states into 4 main regions:

* West
* Northeast
* South
* North Central

```{r, echo=tfecho}
state_index <- as.data.frame(cbind(as.character(state.abb), 
                                   tolower(as.character(state.name)), 
                                   as.character(state.region)))
colnames(state_index) <- c("state", "region", "area")
state_index$state <- as.character(state_index$state)
state_index$region <- as.character(state_index$region)
state_index$area <- as.character(state_index$area)
beers_and_brewery <- merge(beers_and_brewery, state_index, by = "state")
```

Count of beers by region:
```{r, echo=FALSE}
table(beers_and_brewery$area)
```

Count of breweries by region:
```{r, echo=FALSe}
table(unique(beers_and_brewery[,c(10, 18)])$area)
```

Is there a relationship between brewery location and beer types?

* We will conduct a chi-squared test for independence

```{r, echo=tfecho}
regions <- as.factor(beers_and_brewery$area)
beer_type <- as.factor(beers_and_brewery$type)

chisq.test(regions, beer_type)
```

The result is a very low p-value, so we can conclude that there is dependence between regions and beer types. 

To analyze the relationship between characteristics and region, let's map the beer alochol content and IBU by region.

```{r, echo=tfecho, warning=FALSE, message=FALSE}
states <- map_data("state")
states <- left_join(states, state_index)
states <- left_join(states, beers_and_brewery)

abv_region <- aggregate(na.omit(beers_and_brewery[,c(4)]), 
          by = list(region = beers_and_brewery$area[which(!is.na(beers_and_brewery$abv))]), 
          FUN = mean, na.action = na.pass)
colnames(abv_region)[2] <- c("mean_abv")

states <- left_join(states, abv_region, by = "region")

states_abv <- ggplot(data = states) + 
  geom_polygon(aes(x = long, y = lat, fill = mean_abv, group = group), color = "white") + 
  coord_fixed(1.275) +
  guides(fill = FALSE) +
  ggtitle("Map of Regions") +
  theme(plot.title = element_text(hjust = 0.5))
  
```


#KNN
```{r, echo=tfecho}
beers_and_brewery$ibu[which(is.na(beers_and_brewery$ibu))] <- 
  beers_and_brewery$abv[which(is.na(beers_and_brewery$ibu))]

beers_and_brewery <- beers_and_brewery[which(!is.na(beers_and_brewery$abv)), ]

control <- trainControl(method = "cv", number = 10)

rf <- train(type ~ abv + ibu + area + ounces, data = beers_and_brewery, 
                 trControl = control, method = "rf")

table(predict(rf, beers_and_brewery))
table(beers_and_brewery$type)

type_knn <- knn3(x = beers_and_brewery[c(3, 4)], 
                 y = as.factor(beers_and_brewery$type), 
                 formula = type ~ abv + ibu + interaction)
```

#ABV and IBU by Type of Beer
```{r, echo=tfecho}
type_by_abv_and_ibu <- ggplot(data = beers_and_brewery) +
  geom_point(aes(abv, ibu, color = type))
```

#Beer Stats by Brewery
```{r, echo=tfecho, warning=FALSE, message=FALSE}
avg_brewery <- aggregate(beers_and_brewery, list(Brewery = beers_and_brewery$name.y), FUN = mean, na.action = na.omit)
avg_state <- aggregate(beers_and_brewery, list(Brewery = beers_and_brewery$state), FUN = mean, na.action = na.omit)
```

#Maps
```{r, echo=tfecho, message=FALSE, warning=FALSE}
state_index <- as.data.frame(cbind(as.character(state.abb), 
                                   tolower(as.character(state.name)), 
                                   as.character(state.region)))
colnames(state_index) <- c("state", "region", "area")
state_index$state <- as.character(state_index$state)
state_index$region <- as.character(state_index$region)

states <- map_data("state")
states <- left_join(states, state_index)
beers_and_brewery$state <- gsub(" ", "", beers_and_brewery$state)
states <- left_join(states, beers_and_brewery)

states_abv <- ggplot(data = states) + 
  geom_polygon(aes(x = long, y = lat, fill = area, group = group), color = "white") + 
  coord_fixed(1.275) +
  guides(fill = FALSE)
```



